An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-14 paper/paper.tex
Paper: detail starting points for each section and subsection in Background and BTBackup
Enable hyperlinking in the paper

%%\usepackage{setspace}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{alltt}
\usepackage{color}
\usepackage{fancyvrb} 
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{verbatim}
%\usepackage[autostyle]{csquotes} 
%\usepackage[toc,page]{appendix}

@@

@@

The DHT

@@

Signature stuff

@@

@@

Reduction of information leakage

BTSync crypto and security

@@

If less than X number of replicas, a peer should make a new replica on a node that has yet to hold a replica.

@@

@@

\section{}

@@

\subsection{The Data Layer: BitTorrent Sync}

%Cool new tool, implements bittorrent protocol, but unfortunately closed source. in production ready system, would want to open source (possibility of backdoor, etc)

@@

%Simplification: centralized tracker

>>>>

%%\usepackage{setspace}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{alltt}
\usepackage{color}
\usepackage{fancyvrb} 
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{verbatim}
\usepackage{hyperref}
%\usepackage[autostyle]{csquotes} 
%\usepackage[toc,page]{appendix}

@@

\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=black,  %choose some color if you want links to stand out
}

@@

% The DHT (what information would be stored in it)

@@

% Signature stuff in our original DHT design (need to rework this)

@@

% Synchronization software
% Use of BitTorrent

@@

% Reduction of information leakage

% BTSync crypto and security

@@

%If less than X number of replicas, a peer should make a new replica on a node that has yet to hold a replica.

@@

% Introduce terminology: "store" and "back up" (and, further, "node" and "peer")
% People store proportional amount of data compared to how much they are backing up

@@

@@

% BitTorrent Sync as synchronization software
%Cool new tool, implements bittorrent protocol, but unfortunately closed source. in production ready system, would want to open source (possibility of backdoor, etc)

@@

% Simplification: centralized tracker
% simplification: metadataRecord (doesn't hold all the information)
